Tunable Spectral Ordering of Magnetic Plasmon Resonances

### 2018-03-07 paper_winter_2017/draft_winter_2017.tex
new figures, updated draft

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Nicholas P. Montoni}
\author{Steven C. Quillin}
\author{Charles Cherqui}
\author{David J. Maisello}
\affiliation[Department of Chemistry, University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA 98195}
\email{masiello@chem.washington.edu}
\date{September 4, 2017}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]
    {Tunable Spectral Ordering of Magnetic Plasmon Resonances}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{MNP, LSPR, EELS}
\keywords{magnetic plasmons, plasmon metamolecules}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}
\begin{centering}
\includegraphics[width=7cm]{toc.png}
\end{centering}
\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Using first-principles theory and simulated cathodoluminescence spectroscopy, the optical-frequency magnetic resonances of cyclic aromatic and hexagonally packed metal nanoparticle clusters are explored. A fully retarded coupled dipole model is employed, expanding upon past work in the field, to explore the dependence of the resonant frequencies and spectral ordering of the magnetic resonances on cluster size. It is shown that magnetic resonances change spectral order as metal nanoparticle oligomers change in size, and that these mode switches are observable in full-wave numerical electrodynamics simulations of angle-resolved cathodoluminescence spectra. Electron-beam spectroscopies are uniquely suited to observing this phenomenon, as they provide nanometer spatial and sub-eV spectral resolution and can preferentially excite one magnetic resonance over another. Furthermore, angle-resolved spectroscopies leverage the specific radiation patterns attributed to each magnetic plasmon, clearly differentiating spectral signatures of each individual magnetic plasmon resonance.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Clusters of metal nanoparticles (MNPs) that exhibit anomalously strong magnetic fields, called plasmon oligomers or plasmon metamolecules, have been of great interest in recent years. Magnetic plasmon resonances in these systems have been shown to couple to and enhance the magnetic field of light and hybridize analogously to electric plasmon resonances\cite{Alu2006,Alu2008,Dionne2011,Cherqui2014,Dionne2016,Cherqui2016,Engheta2017}. The magnetic properties of single oligomers, i.e. those systems composed of only one ring of MNPs, are now well understood based upon models in the quasistatic limit\cite{Nord2006,Dionne2011,Dionne2016,Capolino2017}. Conversely, the infinite-oligomer regime has also been understood within the language of tight-binding models of solid-state physics\cite{Schatz2003,Weick2013}. Recently, a disconnect between these size regimes and methods has arisen, leading to open questions in how magnetic plasmon resonances behave in few-oligomer assemblies, called the intermediate size regime\cite{NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}.

Most crucial to this disconnect is the question of when and how retardation effects matter. For example, in the case of the two oligomer cluster (the 2-mer) the quasistatic approximation has been shown to deviate from full-wave numerical electrodynamics simulations in that it predicts a different energy-ordering of the magnetic plasmon resonances.\cite{Cherqui2014}. Retardation effects have been incorporated into models of single MNPs\cite{Gu2010}, dimers\cite{vonPlessen2007}, and infinite chains and arrays\cite{Kottman2001,Rechbacher2003,Schatz2003,Royer2005,Abajo2008,Chumanov2010,Pinchuk2016}. However, with the exception of numerical studies, no analytical models include retardation effects in the description of magnetic plasmon oligomers. Here, we show that the incorporation of retardation effects corrects the aforementioned discrepancy between model and simulation, and further points to the facile ability to tune the magnetic plasmon spectrum via scaling oligomer size. This is important because it allows for the facile manipulation of the effective permittivity and permeability thereby facilitating the design of future tunable optical metamaterials. [Pendry superlens, other stuff]

In the following, we demonstrate the evolution of the magnetic plasmon resonances in intermediate-size $n$-mers with scaling by including the full field within a coupled dipole approach describing their interaction. Interestingly, as a function of scaling, the magnetic resonances switch their ordering in analogy to the way that electric plasmon resonances in hybridized nanoparticles can switch order\cite{vonPlessen2007}. We further analyze the distinct radiative properties of each magnetic plasmon resonance by computing the angle-resolved cathodoluminescence (CL) spectrum\cite{Hohenester2012,Coenen2011,CoPol2011,Polman2014}. The spectral ordering depends not only on aggregate scale but also upon oligomer morphology which we examine below. [Reword, superlensing and cloaking!] Tunability of the relative phase of magnetic fields in a single MNP cluster may lead to advances in detection methods\cite{Zia2010trans,Noginova2008trans,Wang:13,Fan2015,Wei2015,Shvets2012,Altug2012bio,Nord2011fano}, anti-reflective coatings\cite{Alu2006,Alu2008}, and information processing\cite{NordHal2011,NordHal2012}.

@@

\begin{figure}
\includegraphics[width=6.5in]{2mer_3mer_fields.pdf}
\caption{Magnetic field plots of the 2mer (a and b) and 3mer (c, d, and e) oligomers. Each system supports a number of closed-loop magnetic plasmon resonances equal to the number of rings in the system. The magnetic plasmons support an electric dipole moment (a, c, and d) support out-of-phase magnetic fields. The nodeless magnetic modes (b and e) support a net magnetic dipole moment are accessible to the magnetic field of light.}
\label{field_plots}
\end{figure}

Figure~\ref{field_plots} displays two model systems, the 2-mer and 3-mer, comprising 10 and 13 silver nanospheres in analogy to naphthalene and phenalene. The mapping of the electric localized surface plasmon resonances of individual noble metal nanoparticles onto harmonic oscillators is now well-understood [lots of cites]. In the limit where each nanoparticle, here restricted to a spherical geometry of radius $a$, possesses only an electric dipole plasmon resonance, the equations of motion dictating the electromagnetic response of the oligomer are

\begin{equation}
\ddot{\textbf{q}}_i = -\omega_{\textrm{sp}}^2\textbf{q}_i + \frac{e}{m_{\textrm{sp}}}\sum_{j\neq i}\textbf{E}_j(\textbf{r}_i),
\label{equation_of_motion}
\end{equation}

\noindent where $\omega_{\textrm{sp}}$ is the natural frequency of the Mie resonance, $m_{\textrm{sp}} = e^2/\alpha_{\textrm{sp}}\omega_{\textrm{sp}}^2$ is the plasmon's effective mass defined in terms of the polarizability $\alpha_{\textrm{sp}} = 3a^3/(\varepsilon_{\infty} + 2\varepsilon_b)$, with $\varepsilon_{\infty}$ and $\varepsilon_b$ the high-frequency and background dielectric functions. The dipole moment of each plasmon oscillator, restricted to lie in the plane of the oligomer at position ri [format], is $\textbf{d}_i = e\textbf{q}_i$ and $\textbf{E}_j(\textbf{r}_i)$ is the fully retarded electric field of the $j^{\textrm{th}}$ dipole evaluated at the position of the $i^{\textrm{th}}$ dipole. It is defined by

\begin{equation}
\textbf{E}_j(\textbf{r}_i) = \boldsymbol{\Lambda}_{ij}\cdot\textbf{d}_j\\
= \left\{\left(\frac{1}{r_{ij}^3} - \frac{ik}{r_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) + \frac{k^2}{r_{ij}}\left(\textbf{1}-\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij}\right)\right\}\frac{e^{\textrm{i}kr_{ij}}}{\varepsilon_b}\cdot\textbf{d}_j,
\label{electric_field_lambda}
\end{equation}

\noindent where, $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two dipoles separated by distance $r_{ij}$, $k=\sqrt{\varepsilon_b}\omega/c$ where $\omega$ is the oscillatory frequency of the $j^{\textrm{rm}}$ dipole. The field is decomposed into three parts: [put in scaling] the near-, intermediate-, and far-field. All dipolar retardation effects are included in this field\cite{Purcell1973}. Due to the relative magnitudes of these terms and the sign of [e to the ikr] the interaction energies can change sign and go from energy-lowering to energy-raising.

As described in the methods section, there are as many normal modes of each N-mer as there are electric dipole plasmons. Of these normal modes, some are electric in character and some are magnetic in character with $n$ magnetic plasmon resonances for each $n$-mer studied here. Figure~\ref{field_plots} shows these magnetic plasmon normal modes overlaid with their associated signed magnetic field magnitude. Each mode is named for its particular magnetic field distribution after the poles of a magnet, either all-North (aN) or North-South (NS). The top right-hand corner of each panel indicates whether the  mode depicted has a net electric dipole or a net magnetic dipole moment. In planar geometries, the magnetic dipole moments are always perpendicular to the in-plane electric dipole moments. As a result, they scatter light with different directionality as will be discussed.

@@

To determine the impact of incorporating retardation effects, it is first useful to consider the quasistatic limit. Here individual particle frequencies (define omegasp) are size independent and the coupling strength depends only upon the scale $s = rij/a$ and not upon the overall oligomer size. That is, if this ratio $s$ of inter-particle distance $r_{ij}$ to particle size $a$ remains constant, as the particles grow the collective frequencies do not change. This is evident by considering the k goes to zero limit of the electric field in Equation~\ref{electric_field_lambda},

\begin{equation}
\begin{aligned}
\frac{e^2}{m_{\textrm{sp}}}\boldsymbol{\Lambda}_{ij} &= \omega_{\textrm{sp}}^2 \alpha_{\textrm{sp}}\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{r_{ij}^3} \\
&= \omega_{\textrm{sp}}^2 \left(\frac{3r_0^3}{\varepsilon_{\infty}+2\varepsilon_b}\right)\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{(sr_0)^3}.
\end{aligned}
\label{quasistatic_coupling}
\end{equation}

\noindent where msp and alphasp are rewritten in terms of fundamental parameters. Retardation effects, however, remove this invariance and introduce size-dependence into both the individual plasmon natural frequency as well as into the electric field. Consequently, in the following we choose the individual MNP radius as the independent variable, fixing the nearest neighbor distance at 3$a$, to investigate the effects of retardation upon the magnetic plasmon spectrum in intermediate-size $n$-mers.

\begin{figure}
\includegraphics[width=4in]{2mer-3mer-eig.pdf}
\caption{Eigenenergies (a and c) and interaction energies (b and d) for the 2mer and 3mer. At small scales $r_0 < 5$ nm the magnetic modes are ordered as predicted using a quasistatic model, with NS (orange) lower in energy than aN (blue). This implies that for very small oligomer systems, the quasistatic approximation is still accurate. However, at sizes greater than $r_0 = 5$ nm and smaller than $r_0 = 20$ nm, the eigenmodes switch order. This is due to the dominance of the far-field term, which is evident from (b and d). Finally, at sizes greater than $r_0 = 20$ nm, the eigenmodes switch order again. Also plotted are simulated peak positions of each mode (dashed lines) to show agreement within 0.1 eV.}
\label{scaling}
\end{figure}

Figure~\ref{scaling} shows the predicted eigenenergies and the simulated spectral peak positions for the magnetic modes of the 2mer and 3mer with varying $r_0$. At small sizes the magnetic modes preserve the quasistatic ordering predicted in previous work, which is to be expected when the oligomer system fits easily into a wavelength of light and the near-field dominates the electric field\cite{Cherqui2014}. In fact, a fully retarded scattering spectrum of an aggregate of this size is qualitatively identical to quasistatic simulations of the same system at all sizes. This implies that the quasistatic approximation is accurate only for magnetic oligomers spanning less than a quarter of the wavelength of light, smaller than suggested by previous work for single particles\cite{Economou1974}. As the system scale increases, the eigenenergies decrease and appear to cross at $r_0 = 7$ nm, and once more at $r_0 = 20$ nm. This is due to the far-field term in Equation~\ref{electric_field_lambda} becoming strong relative to the near- and intermediate-fields, as shown in Figure~\ref{scaling}b and d (squares). As the system gets larger, it takes information longer to propagate across the aggregate, meaning that retardation effects become important. The second crossing of the eigenmodes recovers the ordering at small sizes, which might lead to the erroneous conclusion that the quasistatic approximation is accurate again. Rather, both eigenmode crossings are due entirely to retardation effects. The interaction energy between all the dipoles in each magnetic mode, [reformat equation]

\begin{equation}
U_{\textrm{int}} = -\sum_i \textbf{d}_i \cdot \sum_{j \neq i} \textbf{E}_j(\textbf{r}_i),
\label{interactionenergy}
\end{equation}

\noindent with the same $\textbf{E}_j$ defined in Equation~\ref{electric_field_lambda}, explains why the modes cross at certain system sizes. The inclusion of the far-field, the third term in Equation~\ref{electric_field_lambda} is the cause of the mode switching, as it carries the opposite sign of the near- and intermediate-field terms. These terms with opposite splitting are the cause of the mode crossings; as the near- and intermediate-fields lower the energy of the North-South mode, the far-field raises the energy of the North-South mode, and vice-versa for the North-North mode. Close inspection of Figure~\ref{scaling}b reveals that the crossing points occur where the splitting in the near- and intermediate-fields is equal and opposite to that of the far-field. Perhaps more interestingly, in water the crossing points are shifted towards smaller scale. This is to be expected, as the wavelength of light is compressed in a medium, meaning that light sees objects as much bigger than they really are. This analysis shows that the quasistatic approximation is good for very small magnetic oligomers in vacuum, and for smaller oligomers in medium. This can also be explained through the impact of a dielectric medium on coupling strength. While a medium should contribute an overall increase to the coupling strength (which is predicted in Figure~\ref{scaling}b and f), the far-field term should be more drastically impacted due to its extra $\varepsilon_b$-dependence through its $k^2$ term.\cite{Elsayed2008} Through comparison with simulation (dashed lines in Figure~\ref{scaling}a), it can be shown that this simple and efficient model is accurate to within 0.05 eV and accurately describes the behavior of magnetic plasmon oligomers.

Previous work has explored the oscillatory nature of resonance frequency and radiation damping as a function of size in plasmonic systems\cite{vonPlessen2007}. We have shown that a fully retarded coupled dipole approach predicts magnetic plasmon resonance switching, and explains that it is due to inclusion of the far-field term in the dipole relay tensor. From here, we use simulated angle-resolved CL spectroscopy to observe this magnetic mode switching, leveraging the specific radiative properties of each magnetic plasmon and the ability of the electron beam to isolate specific plasmon modes.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Nicholas P. Montoni}
\author{Steven C. Quillin}
\author{Charles Cherqui}
\author{David J. Maisello}
\affiliation[Department of Chemistry, University of Washington]
{Department of Chemistry, University of Washington, Seattle, WA 98195}
\email{masiello@chem.washington.edu}
\date{February 12, 2017}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[]
    {Tunable Spectral Ordering of Magnetic Plasmon Resonances}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some journals require a list of abbreviations or keywords to be
%% supplied. These should be set up here, and will be printed after
%% the title and author information, if needed.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abbreviations{MNP, LSPR, EELS}
\keywords{magnetic plasmons, plasmon metamolecules}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The "tocentry" environment can be used to create an entry for the
%% graphical table of contents. It is given here as some journals
%% require that it is printed as part of the abstract page. It will
%% be automatically moved as appropriate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tocentry}
\begin{centering}
\includegraphics[height=3.5cm]{toc.png}
\end{centering}
\end{tocentry}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The abstract environment will automatically gobble the contents
%% if an abstract is not used by the target journal.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
Abstract.
%Using first-principles theory and simulated cathodoluminescence spectroscopy, the optical-frequency magnetic resonances of cyclic aromatic and hexagonally packed metal nanoparticle clusters are explored. A fully retarded coupled dipole model is employed, expanding upon past work in the field, to explore the dependence of the resonant frequencies and spectral ordering of the magnetic resonances on cluster size. It is shown that magnetic resonances change spectral order as metal nanoparticle oligomers change in size, and that these mode switches are observable in full-wave numerical electrodynamics simulations of angle-resolved cathodoluminescence spectra. Electron-beam spectroscopies are uniquely suited to observing this phenomenon, as they provide nanometer spatial and sub-eV spectral resolution and can preferentially excite one magnetic resonance over another. Furthermore, angle-resolved spectroscopies leverage the specific radiation patterns attributed to each magnetic plasmon, clearly differentiating spectral signatures of each individual magnetic plasmon resonance.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Start the main part of the manuscript here.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Clusters of metal nanoparticles (MNPs) that exhibit anomalously strong magnetic fields, called plasmon oligomers or plasmon metamolecules, have been of great interest in recent years\cite{Alu2006,Alu2008,Liu2011,Dionne2011,Qian2015,Dionne2016}. Magnetic plasmon resonances in these systems have been shown to couple to and enhance the magnetic field of light and hybridize analogously to electric plasmon resonances\cite{Zhang2006,Zhang2007,NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}. The magnetic properties of single oligomers, i.e. those systems composed of only one ring of MNPs, are now well understood based upon models in the quasistatic limit\cite{Nord2006,Dionne2011,Dionne2016,Capolino2017}. Conversely, the infinite-oligomer regime has also been understood within the language of tight-binding models of solid-state physics\cite{Schatz2003,Weick2013}. Recently, a disconnect between these size regimes and methods has arisen, leading to open questions in how magnetic plasmon resonances behave in few-oligomer assemblies, called the intermediate size regime\cite{NordHal2011,NordHal2012,Cherqui2014,Cherqui2016,Engheta2017}.

Most crucial to this disconnect is the question of when and how retardation effects matter. For example, in the case of the two oligomer cluster (the 2-mer) the quasistatic approximation has been shown to deviate from full-wave numerical electrodynamics simulations in that it predicts a different energy-ordering of the magnetic plasmon resonances.\cite{Cherqui2014}. Retardation effects have been incorporated into models of single MNPs\cite{Gu2010}, dimers\cite{Oubre2004,vonPlessen2007}, and infinite chains and arrays\cite{Lucas1976,ARAVIND1981,Kottman2001,NordHal2003,NordProdan2004,Rechbacher2003,Schatz2003,Royer2005,Abajo2008,Gomez2009,Chumanov2010,Pinchuk2016}. However, with the exception of numerical studies, no analytical models include retardation effects in the description of magnetic plasmon oligomers. Here, we show that the incorporation of retardation effects corrects the aforementioned discrepancy between model and simulation, and further points to the facile ability to tune the magnetic plasmon spectrum via scaling oligomer size. This is important because it allows for the facile manipulation of the effective permittivity and permeability thereby facilitating the design of future tunable optical metamaterials.

In the following, we demonstrate the evolution of the magnetic plasmon resonances in intermediate-size $N$-mers with size by including the full field within a coupled dipole approach describing their interaction. Interestingly, as a function of size, the magnetic resonances switch their ordering in analogy to the way that electric plasmon resonances in hybridized nanoparticles can switch order\cite{vonPlessen2007}. We further analyze the distinct radiative properties of each magnetic plasmon resonance by computing the angle-resolved cathodoluminescence (CL) spectrum\cite{Hohenester2014,Coenen2011,CoPol2011,Polman2014}. The spectral ordering depends not only on aggregate size but also upon oligomer morphology which we examine below. The ability to choose the resonance frequency of specific magnetic plasmon resonances will lead to advances in superlensing and electromagnetic cloaking at optical frequencies, as these applications stem directly from tunable negative-index metamaterials\cite{Pendry03,Fang2005,Cai2007,Pinchuk07,Shalaev2008,Valentine2008,Ferrari09}.

@@

\begin{figure}
\includegraphics{2mer_3mer_fields.pdf}
\caption{Magnetic field plots of the 2mer (a and b) and 3mer (c, d, and e) oligomers. Each system supports a number of closed-loop magnetic plasmon resonances equal to the number of rings in the system. The magnetic plasmons support an electric dipole moment (a, c, and d) support out-of-phase magnetic fields. The nodeless magnetic modes (b and e) support a net magnetic dipole moment are accessible to the magnetic field of light.}
\label{field_plots}
\end{figure}

Figure~\ref{field_plots} displays two model systems, the 2-mer and 3-mer, comprising 10 and 13 silver nanospheres in analogy to naphthalene and phenalene. The mapping of the electric localized surface plasmon resonances of individual noble metal nanoparticles onto harmonic oscillators is now well-understood\cite{ARPC}. In the limit where each nanoparticle, here restricted to a spherical geometry of radius $a$, possesses only an electric dipole plasmon resonance, the equations of motion dictating the electromagnetic response of the oligomer are

\begin{equation}
\ddot{\textbf{q}}_i = -\omega_{\textrm{sp}}^2\textbf{q}_i + \frac{e}{m_{\textrm{sp}}}\sum_{i,j\neq i}\textbf{E}_j(\textbf{r}_i),
\label{equation_of_motion}
\end{equation}

\noindent where $\omega_{\textrm{sp}}$ is the natural frequency of the Mie resonance, $m_{\textrm{sp}} = e^2/\alpha_{\textrm{sp}}\omega_{\textrm{sp}}^2$ is the plasmon's effective mass defined in terms of the polarizability $\alpha_{\textrm{sp}} = 3a^3/(\varepsilon_{\infty} + 2\varepsilon_b)$, with $\varepsilon_{\infty}$ and $\varepsilon_b$ the high-frequency and background dielectric functions. The dipole moment of each plasmon oscillator, restricted to lie in the plane of the oligomer at position $\textbf{r}_i$, is $\textbf{d}_i = e\textbf{q}_i$ and $\textbf{E}_j(\textbf{r}_i)$ is the fully retarded electric field of the $j^{\textrm{th}}$ dipole evaluated at the position of the $i^{\textrm{th}}$ dipole. The electric field is defined by

\begin{equation}
\textbf{E}_j(\textbf{r}_i) = \boldsymbol{\Lambda}_{ij}\cdot\textbf{d}_j\\
= \left\{\left(\frac{1}{r_{ij}^3} - \frac{ik}{r_{ij}^2}\right)\left(3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right) - \frac{k^2}{r_{ij}}\left(\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}\right)\right\}\frac{e^{\textrm{i}kr_{ij}}}{\varepsilon_b}\cdot\textbf{d}_j,
\label{electric_field_lambda}
\end{equation}

\noindent where, $\hat{\textbf{n}}_{ij}$ is the unit vector connecting two dipoles separated by distance $r_{ij}$, $k=\sqrt{\varepsilon_b}\omega/c$ where $\omega$ is the oscillatory frequency of the $j^{\textrm{th}}$ dipole. Interestingly, the far-field term carries the opposite sign of the near-field term. The field is decomposed into three parts: the near- ($r_{ij}^{-3}$), intermediate- ($r_{ij}^{-2}$), and far-field ($r_{ij}^{-1}$). All dipolar retardation effects are included in this field\cite{Purcell1973}. Due to the relative magnitudes of these terms and the sign of $e^{\textrm{i}kr_{ij}}$ the interaction energies can change sign and go from energy-lowering to energy-raising.

As described in the methods section, there are as many normal modes of each N-mer as there are electric dipole plasmons. Of these normal modes, some are electric in character and some are magnetic in character with $N$ magnetic plasmon resonances for each $N$-mer studied here. Figure~\ref{field_plots} shows these magnetic plasmon normal modes overlaid with their associated signed magnetic field magnitude. Each mode is named for its particular magnetic field distribution after the poles of a magnet, either all-North (aN) or North-South (NS). The top right-hand corner of each panel indicates whether the  mode depicted has a net electric dipole or a net magnetic dipole moment. In planar geometries, the magnetic dipole moments are always perpendicular to the in-plane electric dipole moments. As a result, they scatter light with different directionality as will be discussed.

@@

To determine the impact of incorporating retardation effects, it is first useful to consider the quasistatic limit. Here individual particle frequencies (define omegasp) are size independent and the coupling strength depends only upon the scale $s = r_{ij}/a$ and not upon the overall oligomer size. That is, if this ratio $s$ of inter-particle distance $r_{ij}$ to particle size $a$ remains constant, as the particles grow the collective frequencies do not change. This is evident by considering the k goes to zero limit of the electric field in Equation~\ref{electric_field_lambda},

\begin{equation}
\begin{aligned}
\lim_{k \to 0}\textbf{E}_j(\textbf{r}_i) &= \frac{e^2}{m_{\textrm{sp}}}\boldsymbol{\Lambda}_{ij}\\ 
&= \frac{\omega_{\textrm{sp}}^2 \alpha_{\textrm{sp}}^2}{\varepsilon_b}\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{r_{ij}^3} \cdot \textbf{d}_j \\
&= \frac{\omega_{\textrm{sp}}^2}{\varepsilon_b} \left(\frac{3}{\varepsilon_{\infty}+2\varepsilon_b}\right)\frac{3\hat{\textbf{n}}_{ij}\hat{\textbf{n}}_{ij} - \textbf{1}}{s^3} \cdot \textbf{d}_j
\end{aligned}
\label{quasistatic_coupling}
\end{equation}

\noindent where $m_{\textrm{sp}}$ and $\alpha_{\textrm{sp}}$ are rewritten in terms of fundamental parameters for silver: $\varepsilon_{\infty} = 3.77$, $\hbar\gamma = 0.05$ eV, and $\hbar\omega_{p} = 9.1$ eV. Retardation effects, however, remove this invariance and introduce size-dependence into both the individual plasmon natural frequency as well as into the electric field. Consequently, in the following we choose the individual MNP radius $a$ as the independent variable, fixing the nearest neighbor distance at 3$a$, to investigate the effects of retardation upon the magnetic plasmon spectrum in intermediate-size $N$-mers.

\begin{figure}
\includegraphics{2mer-3mer-eig.pdf}
\caption{Eigenenergies (a and c) and interaction energies (b and d) for the 2mer and 3mer. At small scales $r_0 < 5$ nm the magnetic modes are ordered as predicted using a quasistatic model, with NS (orange) lower in energy than aN (blue). This implies that for very small oligomer systems, the quasistatic approximation is still accurate. However, at sizes greater than $r_0 = 5$ nm and smaller than $r_0 = 20$ nm, the eigenmodes switch order. This is due to the dominance of the far-field term, which is evident from (b and d). Finally, at sizes greater than $r_0 = 20$ nm, the eigenmodes switch order again. Also plotted are simulated peak positions of each mode (dashed lines) to show agreement within 0.1 eV.}
\label{scaling}
\end{figure}

Figure~\ref{scaling} shows the predicted resonance energies from both the model and full-wave optical simulations of the 2-mer and 3-mer with increasing $a$.\cite{Hohenester2012} At small sizes the magnetic modes preserve the quasistatic ordering predicted in previous work, which is to be expected when the oligomer system fits within a wavelength of light and the near-field dominates the electric field\cite{Cherqui2014}. As the system size increases, the resonance energies decrease and to cross at $a = 7$ nm, and once more at $a = 20$ nm. This is due to the far-field contribution in Equation~\ref{electric_field_lambda} becoming large relative to the near- and intermediate-fields, as shown in Figure~\ref{scaling}b and d (squares). The second crossing of the eigenmodes recovers the ordering at small sizes, which might lead to the erroneous conclusion that the quasistatic approximation is accurate again. Rather, both eigenmode crossings are due entirely to retardation effects. The interaction energy between all the dipoles in each magnetic mode, [reformat equation]

\begin{equation}
U_{\textrm{int}} = -\frac{1}{2} \sum_{ij} \textbf{d}_i \cdot \textbf{E}_j(\textbf{r}_i),
\label{interactionenergy}
\end{equation}

\noindent with the same $\textbf{E}_j$ defined in Equation~\ref{electric_field_lambda}, explains why the modes cross at certain system sizes. The inclusion of the far-field, the third term in Equation~\ref{electric_field_lambda} is the cause of the mode switching, as it carries the opposite sign of the near- and intermediate-field terms. These terms with opposite splitting are the cause of the mode crossings; as the near- and intermediate-fields lower the energy of the North-South mode, the far-field raises the energy of the North-South mode, and vice-versa for the North-North mode. Close inspection of Figure~\ref{scaling}b reveals that the crossing points occur where the splitting in the near- and intermediate-fields is equal and opposite to that of the far-field. Perhaps more interestingly, in any dielectric medium with $\varepsilon_b > 1$ the crossing points are shifted towards smaller scale due to wavelength contraction. This can also be explained through the impact of a dielectric medium on coupling strength. While a medium should contribute an overall increase to the coupling strength, the far-field term should be more drastically impacted due to its extra $\varepsilon_b$-dependence through its $k^2$ term.\cite{Elsayed2008}

Previous work has explored the oscillatory nature of hybridized electric dipole plasmon resonance frequencies and radiation damping as a function of separation in noble metal dimers\cite{vonPlessen2007}. Analogously, our work shows that magnetic plasmon resonance energies also oscillate with interparticle separation and can be understood via analysis of the contributions to the dipole-dipole interaction.

\section{Radiative Properties of Magnetic Plasmon Resonances}
Only those magnetic resonances supporting net electric or magnetic dipole moments will radiate to the far field. The magnetic dipole moment of the aN magnetic mode is perpendicular to the electric dipole moment(s) of the NS mode in both the model 2-mer and 3-mer. This means that these modes radiate with different directionality. It has been predicted and shown experimentally that 1-mers scatter light anisotropically when both their magnetic dipole moment and electric dipole moment are mutually excited,\cite{Dionne2011,Cherqui2016} as is evident in differential scattering spectra and profiles. Both observations stem from the differential power,\cite{jackson_classical_1999,schwinger1998classical}
